---
title: "Introduction to Animaniac"
author: Seungjun Ahn
date: November 21, 2019
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(animaniac)
```

## 1. Introduction
In general, we create multiple plots to see how our results would change over time or varing with some adjustments. We normally include them as subfigures in a paper. Data visualizations are without doubt very helpful summarizing the data, but it may not efficiently do so, when there are excessive numbers of them. \

Thus, I wanted to create a package that produces a single plot visualizing changes or patterns more dynamically -- i.e. animated plot. In particular, this package enables generating an animated histogram with a smoothing curve which varies with its bandwidth specification (bandwidth min/max and number of bandwidth). `iris` dataset is used for the example. The package can also be utilized for creating an animated barplot, summarizing the pattern for the specified duration. An example dataset (`SanMartinoPPts` from package `hydroTSM`) is provided for a better understanding of this.


## 2. Install animaniac from Github using devtools package
```{r chunk_name, results="hide"}
devtools::install_github("sjahnn/animaniac", force=TRUE)
```
<p style="color:red"> **ATTENTION**: Please create a new folder and make it as your working directory with setwd(), you use this package. Otherwise, it will be hard to keep track. </p>

## 3. Animated Histogram with Kernal Density Estimates (animated.hist.kernel)
```{r}
animated.hist.kernel(x=iris$Sepal.Length, nbreaks=30, bw.min=0.1, bw.max=0.5, bw.n=20, outputname="animated1")
```
You can change `nbreaks` and bandwidth specifications (namely `bw.min`, `bw.max`, and `bw.n`). The example code will generate 20 (default) animated histograms, and it illustrates that larger bandwidth specificiation leads to smoother (flat) density estimates. Conversely, a histogram with a smaller bandwidth specificiation has more localized density estimates. \

Check your working directory. You will be able to find 20 plots (in PNG format) and an animated plot (in GIF format).

<p style="color:red"> **NOTE#1**: If you prefer to have the animated plot ONLY, you can do so with the following: </p>

```{r, eval=FALSE, echo=TRUE} 
file.remove(list.files(pattern=".png"))
```

<p style="color:red"> However, this will delete all of your PNG files in the specified working directory, so make sure you create a new folder before you work with this package. </p> \

<p style="color:red"> **NOTE#2**: For Mac users, you will need to open your generated animated plot (in GIF format) with Safari (Right Click, Open With, then Select Safari). </p>

## 4. Animated Monthly Plot (animated.monthly.report)
```{r}
animated.monthly.report(data=SanMartinoPPts, start.date="1970-01-01", end.date="1989-12-31", months=1:12, outputname="animated2")
```
`SanMartinoPPts` was used as an example dataset to create an animated monthly plot. The dataset is from `hydroTSM` package, and contains a record of daily precipitation from January 1st, 1921 to December 31st 1990, measured at San Martino di Castrozza, Trento Province, Italy. `animated.monthly.report` will generate an animated barplot for the specified duration. The example code will print out 20 barplots (one plot for each year; therefore, total 20 plots for 1970-1989), summarizing precipitation for the specified month, adjustable `months` option. \


Again, you will not be able to see the output in R. Please check your working directory to view your plots.

<p style="color:red"> **NOTE#1** In case, you want to keep your animated barplot ONLY, please refer to NOTE#1 for Animated Histogram. </p> \

<p style="color:red"> **NOTE#2**: For Mac users, you will need to open your generated animated plot (in GIF format) with Safari (Right Click, Open With, then Select Safari). </p>
